Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-10 paper/tex/methods.tex
edited SkyNet

In this study, we used \annz-v.2.0.4 to output only the result of the ANN algorithm.
\Pzpdf s were produced by running an ensemble of 5 ANNs with 6 $ugrizy$ inputs, 2 hidden layers with 12 nodes each, and 1 output of redshift).
Each of the five ANNs was trained with different random seeds for the initialization of input parameters.
Additionally, all ANNs were trained on only a $i \leq 25.3$ subsample of the DC1 training set, and half of the training set was reserved for validation to prevent overfitting.
Undetected galaxies were excluded from the training set, and per-band non-detections in the test set were replaced with the mean magnitude in that band within the entire test set.

@@

\textsc{SkyNet}\footnote{\url{http://ccpforge.cse.rl.ac.uk/gf/project/skynet/}} \citep{Graff:14} is a publicly available neural network software, based on a 2nd order conjugate gradient optimization scheme \citep[see][for further details]{Graff:14}. %It has been used efficiently for redshift PDF estimates \citep{Sanchez:14,Bonnett:15,Bonnett:16}.

%In the present work, we use \textsc{SkyNet} both as a regressor (for redshift point estimates) and a classifier (for PDF estimates).
The neural network is configured as a standard multilayer perceptron with three hidden layers and one input layer with $12$ nodes (the $6$ magnitudes and their errors).
%For the regressor, the output layer is a single linear node, while each hidden layer has $10$ nodes with a tanh activation function.
The classifier is laid out such that the hidden layers have 20:40:40 nodes each, all rectified linear units, and the output layer has $200$ nodes (corresponding to 200 bins for the PDF) activated with a ``softmax'' function so that they automatically sum to $1$.
While previous implementations of the code, such as \citet{Sanchez:14} and \citet{Bonnett:15} (see Appendix C.3), implement a ``sliding bin'' smoothing, no such procedure was used in this study.

To avoid over-fitting, a $30$ per cent fraction of the training set is used as validation, and the training is stopped as soon as the error rate begins to increase in the validation set.
The weights are randomly initialized based on normal sampling.
The error function is a standard chi-square function for the regressor, and a cross-entropy function for the classifier.
Finally, the data are all whitened before processing, with magnitudes pegged to (45,45,40,35,42,42) and their errors pegged to (20,20,10,5,15,15) for $ugrizy$ filters, respectively.

>>>>

In this study, we used \annz-v.2.0.4 to output only the result of the ANN algorithm.
\Pzpdf s were produced by running an ensemble of 5 ANNs with a $6:12:12:1$ architecture corresponding to the 6 $ugrizy$ inputs, 2 hidden layers with 12 nodes each, and 1 output of redshift.
Each of the five ANNs was trained with different random seeds for the initialization of input parameters.
Additionally, all ANNs were trained on only a $i \leq 25.3$ subsample of the DC1 training set, and half of the training set was reserved for validation to prevent overfitting.
Undetected galaxies were excluded from the training set, and per-band non-detections in the test set were replaced with the mean magnitude in that band within the entire test set.

@@

\skynet \footnote{\url{http://ccpforge.cse.rl.ac.uk/gf/project/skynet/}} \citep{Graff:14} employs a neural network based on a second order conjugate gradient optimization scheme \citep[see][for further details]{Graff:14}. %It has been used efficiently for redshift PDF estimates \citep{Sanchez:14,Bonnett:15,Bonnett:16}.
The neural network is configured as a standard multilayer perceptron with three hidden layers and one input layer with 12 nodes corresponding to the 6 photometric magnitudes and their measurement errors.
We use \skynet\ as a regressor for \pz\ point estimation and as a classifier for \pzpdf\ estimation.

The regressor used a standard \chisq\ error function with a single linear node as the output layer and 10 nodes with a $\tanh$ activation function for each hidden layer.
The classifier used a cross-entropy error function with a 20:40:40 node (all rectified linear units) architecture for each hidden layer and an output layer of 200 nodes corresponding to 200 bins for the PDF, with a softmax activation function to enforce the normalization condition that the probabilities sum to unity.
While previous implementations of the code \citep[see Appendix C.3 of~][]{Sanchez:14,Bonnett:15} implement a sliding bin smoothing, no such procedure was used in this study.

We pre-whitened the data by pegging the magnitudes to (45,45,40,35,42,42) and errors to (20,20,10,5,15,15) for $ugrizy$ filters, respectively.
% NO CLUDE WHAT THIS MEANS
To avoid over-fitting, $30\%$ of the training set was reserved for validation, and training was halted as soon as the error rate began to increase on the validation set.
The weights were randomly initialized based on normal sampling.
% WHAT WEIGHTS?
